\documentclass{jdf}

\begin{document}
Section: PUBP-6727
\title{Mutual Monitoring in the Cloud}
\author{Alexander Stein}

\maketitle
\thispagestyle{fancy}

\section{Problem Statement}

Cloud computing infrastructure is essentially ubiquitous, but adoption is not without challenges. Cloud service providers must cater to customers in regulated sectors, complying with cybersecurity frameworks that create high barriers to entry. One barrier is ongoing evaluation of the provider's cybersecurity posture, often resulting in centralized bureaucracies. FedRAMP oversees and documents a prominent example of such a program, the Continuous Monitoring Program.

Are these bureaucracies an optimal solution, or a last resort that fails to keep pace with cloud technology as it proliferates and evolves? If they are a last resort, is there a better way?

\section{Solution Statement}

I will use this research to design and evaluate an alternative to centralized continuous monitoring, mutual monitoring. The foundation of mutual monitoring will be federated data services, known in other security use cases as transparency services. The services will necessarily change cloud service provider and customer behavior, while also incentivizing auditors to sell value-add analytics services in these data services, and possibly obsolete centralized authorities like FedRAMP.

\section{Completed Tasks (Last 2 Weeks)}

\section{Tasks for the Next Project Report}

\section{Questions or issues I'm having}

\section{Methodology Paragraph Summary}

\section{Timeline}

\begin{table}[h]
\begin{tabularx}{\textwidth}{|l|X|l|}
    \hline
    Week \# & Description of Task & Status \\ [0.5ex] 
    \hline
    W1 & Initialize code repository for prototype service & Complete \\
    \hline
    W1 & Present proposal to advisors and integrate feedback; obtain commitment from advisors & In Progress \\
    \hline
    W1 & Read FedRAMP documentation for ConMon processes & In Progress \\
    \hline
    W1 & Begin outline of FedRAMP ConMon critical analysis & In Progress \\
    \hline
\end{tabularx}
\end{table}

\section{Evaluation}

\section{Report Outline}

\section{References}

\nocite{*}
\bibliographystyle{apacite}
\bibliography{references.bib}

\section{Appendix}

\end{document}
